Cryptanalysis of SBC based post-quantum signature scheme

### 2025-05-30 rapport.tex
fini complexité spatiale crossbred

		First, we need to construct $Mac_{\leq D, \geq d, m}^k$ and $\mathcal{M}_{\leq D, \geq d, m}^k$, but the second is by definition a sub matrix of the first, so we would only need to construct the first. We can construct $\mathcal{M}_{\leq D, \geq d, m}^k$ by only manipulating pointers on $Mac_{\leq D, \geq d, m}^k$ for example. So, the important memory footprint that we need to consider in the first part is the one of $Mac_{\leq D, \geq d, m}^k$. Let us consider the following cases
		\begin{itemize}
			\item We use the sparse representation. Then we can use the CSR representation which needs to store an array of column index of the non-zero $col\_index$ elements and an array containing the number of non-zero elements per row $row\_index$. We do not need a third array of coefficients because all the non-zero coefficients are equal to 1.
			The size of $col\_index$ is $nnz$ and the size of $row\_index$ is the number of rows of the matrix.
			So, the memory footprint for the storage of $Mac_{\leq D, \geq d, m}^k$ is in our case
			$$
				memory\_footprint \leq \left(\left(\frac{n^2}{4} + \frac{n}{2} + 1\right) + 1\right) \times \left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m \times 4 \text{ bytes}.
			$$
			One important thing to take into account is the size of the coefficients in the arrays. They have to be at least of size $log\left(\sum_{i=0}^{D} \binom{n}{i}\right)$ \textbf{à affiner comme borne}, because it's the number of columns of $Mac_{\leq D, \geq d, m}^k$. So the most accurate estimation is rather
			$$
				memory\_footprint \leq \left(\left(\frac{n^2}{4} + \frac{n}{2} + 1\right) + 1\right) \times \left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m \times log\left(\sum_{i=0}^{D} \binom{n}{i}\right) \text{ bytes}.
			$$
			\item If we use dense representation, then we could
		\end{itemize}

>>>>

		First, we need to construct $Mac_{\leq D, \geq d, m}^k$ and $\mathcal{M}_{\leq D, \geq d, m}^k$, but the second is by definition a sub matrix of the first, so we would only need to construct the first. We can construct $\mathcal{M}_{\leq D, \geq d, m}^k$ by only manipulating pointers on $Mac_{\leq D, \geq d, m}^k$ for example. So, the important memory footprint that we need to consider in the first part is the one of $Mac_{\leq D, \geq d, m}^k$. Let us consider the following cases
		\begin{itemize}
			\item We use the sparse representation. Then we can use the CSR representation which needs to store an array of column index of the non-zero $col\_index$ elements and an array containing the number of non-zero elements per row $row\_index$. We do not need a third array of coefficients because all the non-zero coefficients are equal to 1.
			The size of $col\_index$ is $nnz$ and the size of $row\_index$ is the number of rows of the matrix.
			So, the memory footprint for the storage of $Mac_{\leq D, \geq d, m}^k$ is in our case
			$$
				memory\_footprint \leq \left(\left(\frac{n^2}{4} + \frac{n}{2} + 1\right) + 1\right) \times \left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m \times 4 \text{ bytes}.
			$$
			One important thing to take into account is the size of the coefficients in the arrays. They have to be at least of size $log\left(\sum_{i=0}^{D} \binom{n}{i}\right)$ \textbf{à affiner comme borne}, because it's the number of columns of $Mac_{\leq D, \geq d, m}^k$. So the most accurate estimation is rather
			$$
				memory\_footprint \leq \left(\left(\frac{n^2}{4} + \frac{n}{2} + 1\right) + 1\right) \times \left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m \times \lceil \lceil log\left(\sum_{i=0}^{D} \binom{n}{i}\right) \rceil \times \frac{1}{8} \rceil \text{ bytes}.
			$$
			\begin{example}
				If we have $D = 12, d = 10, n = 256, m = 257, k=176$, the memory\_footprint would be aboult
				$$
					\left(\left( \frac{256^2}{4} + \frac{256}{2} + 1 \right) + 1 \right) \times \left(\sum_{i=0}^{12} \binom{256}{i} - \sum_{i=0}^{8} \binom{176}{i}\right) \times 257 \times \lceil \lceil log\left(\sum_{i=0}^{12} \binom{256}{i}\right) \rceil \times \frac{1}{8} \rceil = $$ $$ 5112102637167689483266493844 \approx 2^{92} \text{ bytes}.
				$$
			\end{example}
			\item If we use dense representation, then we could represent each row as a single integer of size $log\left(\sum_{i=0}^{D} \binom{n}{i}\right)$ bits and we would have $\left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m$ of these integers, which is the number of rows. So the memory\_footprint would be
			$$
				memory\_footprint \leq \lceil \lceil log\left(\sum_{i=0}^{D} \binom{n}{i}\right) \rceil \times \frac{1}{8} \rceil \times \left(\sum_{i=0}^{D}\binom{n}{i} - \sum_{i=0}^{d-2}\binom{k}{i}\right)m \text{ bytes}.
			$$
			\begin{example}
				If we apply the same last example, this time the footprint would be
				$$
					\lceil \lceil log\left(\sum_{i=0}^{12} \binom{256}{i}\right) \rceil \times \frac{1}{8} \rceil \times \left(\sum_{i=0}^{12}\binom{256}{i} - \sum_{i=0}^{8}\binom{176}{i}\right) \times 257 = $$ $$ 309561743803299593270346 \approx 2^{78} \text{ bytes}.
				$$
			\end{example}
		\end{itemize}
